Condition-Based Maintenance for Complex Systems\\ based on Current Component Status\\ and Bayesian Updating of Component Reliability

### 2017-05-11 cbm-rbd-paper.tex
first part of sec 5 rewritten

@@

When the `optimal' next evaluation moment is before the next planned evaluation moment, we replace the system now;
else we wait for the next planned evaluation moment.
The reason behind this decision is that $\delta$ is taken as %usually is 
%the shortest interval for which re-evaluation of the system RLD will show any difference***
%the shortest inter-observation period that can be realized from a hardware point of view.
the shortest inter-evaluation period that can be realized from a hardware point of view*** / 
the time granularity according to which maintenance actions can be reasonably triggered***.
To illustrate, for component with lifetimes measuring in days,
$\delta$ should be in the order of minutes;
for components with lifetimes measuring in months,
$\delta$ could be one day.

@@

%***start with $\tausnow$???
Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Figure~\ref{fig:timeline} shows two example time lines for the system,
starting each with a new system (operational cycle) at t=0.
As described in Section~\ref{intro},
the health of the system is re-evaluated at

two kinds of triggers

health of system via $\tausnow$, which is described in detail in Section~***

In the left timeline example,

***explain figure, triggers 1, 2, 3***

Consider a set of evaluation time points $\tnow$.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for each present time $\tnow$,
the adaptive and dynamic time span $\tausnow$ which gives the time from $\tnow$ until the optimal moment of maintenance.
Close to system startup, $\tausnow$ will be large;
but as components in the system age and some indeed fail over time,
$\tausnow$ will typically decrease.
%Let $\tprep$ be the time span needed to prepare maintenance work.
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
A preventive maintenance action is initiated
as soon as $\tausnow$ decreases below the time span to the next evaluation time.
%continuing to the the next evaluation point $\tnow$ would carry the risk 
%a time span chosen to reflect operational practicalities.
This dynamic and adaptive maintenance policy is described in more detail in Section~\ref{sec:operationalprocedure};
a flow chart for the policy is given in Figure~\ref{fig:procedure}.

The optimal time to maintenance $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
An operational cycle begins with system start-up,
and ends when either preventive maintenance is carried out,
or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is determined in this situation.
%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
%and a small simulation study is presented in Section~\ref{sec:sim}.

\begin{figure}
\centering
\begin{tikzpicture}
%[tausnow/.style={|-|, line width=0.5mm}]
[ tausnow/.style={line width=0.8mm},
  pfeil/.style={-latex', line width=0.5mm, shorten >=1mm}] 
\draw[-latex', very thick] (-0.2, -0.5) -- (5.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3, 4, 5}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (5,5);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw[tausnow] (2  , 2  ) -- (4.2, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw (2.4, -0.5) circle (0.8mm) edge[dotted] (2.4, 2.4);
%\node[draw,shape=diamond] (f1) at (2.4, -0.4) {}; % edge[dotted] (2.4, 2.4);
\draw[tausnow] (2.4, 2.4) -- (3.9, 2.4) node[at start, left] {$\tau_*^{(0.24)}$};
\draw[tausnow] (3  , 3  ) -- (4.4, 3  ) node[at start, left] {$\tau_*^{(0.3)}$};
\draw (3.6, -0.5) circle (0.8mm) edge[dotted] (3.6, 3.6);
\draw[tausnow] (3.6, 3.6) -- (4.3, 3.6) node[at start, left] {$\tau_*^{(0.36)}$};
\draw[tausnow] (4  , 4  ) -- (4.7, 4  ) node[at start, left] {$\tau_*^{(0.4)}$};
\node (box1) at (1,4) {\parbox{12ex}{\small preventive\\ replacement\\ at $\tnow = 0.4$\\ as $\tau_*^{(0.4)} < \delta$}};
\draw[pfeil] (box1) edge[out=20, in=120] (4,4);
\begin{scope}[xshift=7cm]
\draw[-latex', very thick] (-0.2, -0.5) -- (3.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (3,3);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw (1.4, -0.5) circle (0.8mm) edge[dotted] (1.4, 1.4);
\draw[tausnow] (1.4, 1.4) -- (2.8, 1.4) node[at start, left] {$\tau_*^{(0.14)}$};
\draw[tausnow] (2  , 2  ) -- (3.3, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw[fill] (2.7, -0.5) circle (0.8mm) edge[dotted] (2.7, 2.7);
\node (box2) at (1,4) {\parbox{13ex}{\small corrective\\ replacement\\ at $\tnow = 0.27$\\ due to system failure}};
\draw[pfeil] (box2) edge[out=10, in=90] (2.7,2.7);
\end{scope}
\end{tikzpicture}
\caption{Two exemplary timelines for the suggested maintenance policy.
The horizontal bars depict, for subsequent times $\tnow$,
the time to the next economically optimal inspection $\tausnow$.
The times $\tnow$ for which $\tausnow$ is evaluated are
at regular intervals $\delta, 2\delta, 3\delta,\ldots$ (trigger 1),
and at the time of component failures (trigger 2),
marked by a circle on the time axis.
Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.
The calculation of $\tausnow$ is described in detail in Section~***.}
%\begin{tikzpicture}\draw (0,0) circle (0.8mm);\end{tikzpicture}
\label{fig:timeline}
\end{figure}

@@

\subsection{Detailed description of the policy}
\label{sec:operationalprocedure}

Define a grid of planned evaluation time points as $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.

Frequent recalculation of $\tausnow$ is feasible
when computation of the RLD is fast.
Then, by evaluating the unit cost rate function $\gnow(\tau)$ on a discrete grid,
$\tausnow$ can be approximated with a simple grid search.
%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
%and determine $\tausnow$ with a simple grid search.
Updating $\tausnow$ frequently is useful because,
even in absence of failures of system components,
all components age, and also non-failure adds information to the component models.
%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
%An alternative would be to update $\tausnow$ only when a component fails,
%but as a (near) real-time update of $\tausnow$ is possible and useful,
%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
%
The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance.
However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
our policy is adaptive and dynamic like a CBM policy. 
%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
%but also capable of indicating when corrective maintenance is the better option.
%i.e., capable of choosing the maintenance policy.

@@

In both cases, we decide to maintain the system preventively
when the optimal time to maintenance is closer to now than the next time we intend to re-evaluate $\tausnow$,
since otherwise, in waiting to the next evaluation time,
one would exceed the optimal system failure risk 
as determined by the trade-off made by $\gnow(\cdot)$.
When $\tausnow$ is instead further in the future than the next planned evaluation time,
we can safely continue to the next evaluation time,
without risking to miss the cost-optimal moment to preventively maintain the system.

At the end of each operational cycle, i.e.,
after maintaining the system either preventively or correctively,
the component information gained during the completed operational cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the next operational cycle
account for the (censored) lifetimes observed during the previous operational cycle.
%We assume that both planned and unplanned maintenance action takes negligible time,

Figure~\ref{fig:procedure} displays the flowchart for the policy,
indicating the decisions that are repatedly encountered in a single operational cycle.
The flowchart also contains the loop back to system startup that starts a new operational cycle.

We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
such that the system begins a new operational cycle always under the same conditions.
Replacement schemes that do not replace all components would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper,
since optimizing over replacement schemes is, in our view, a higly interesting topic
that merits an investigation of its own,
and we will comment on this in the conclusion (Section~\ref{sec:outlook}).
%
%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
%does not matter directly for the determination of $\tausnow$.
%Longer downtime and other negative effects of corrective maintenance
%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
%as described next.

@@

To determine the optimal time to maintenance $\tausnow$,
we use the expected one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
as the unit cost rate.
Although a different, renewal theory based way to calculate the unit cost rate is often used
in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation,
where $\tausnow$ changes continuously.

>>>>

\newcommand{\tausfun}[1]{\tau_*^{(#1)}}

@@

When the `optimal' next evaluation moment is before the next planned evaluation moment, we replace the system now;
else we wait for the next planned evaluation moment.
The reason behind this decision is that $\delta$ is taken as %usually is 
%the shortest interval for which re-evaluation of the system RLD will show any difference***
%the shortest inter-observation period that can be realized from a hardware point of view.
the shortest inter-evaluation period that can be realized from a hardware point of view*** / 
the time granularity according to which maintenance actions can be reasonably triggered***.
To illustrate, for components with lifetimes measuring in a few days,
$\delta$ could be in the order of minutes;
for components with lifetimes measuring in months,
$\delta$ could be one day.

@@

%***start with $\tausnow$???
Now we can derive the adaptive and dynamic maintenance policy
that resembles a CBM policy.
Our idea is described here first in general terms,
and then illustrated along two examplary timelines in Section~\ref{sec:policy-example}.
Afterwards, we introduce the formal definition of the policy in Section~\ref{sec:operationalprocedure}***,
and give further details on the involved computations in Sections~\ref{sec:costrate} and \ref{sec:optim}.***

We denote by $\tnow$ the moment in time that the system is observed,
measured from the moment the present operational cycle has started,
which coincides with starting to use a new system.
Instead of determining a threshold for a degradation signal like in usual CBM approaches,
we determine, for $\tnow$, the adaptive and dynamic time span $\tausnow$
which gives the time from $\tnow$ until the next optimal moment to re-evaluate the system.
%Close to system startup, $\tausnow$ will be large;
%but as components in the system age and some indeed fail over time,
%$\tausnow$ will typically decrease.
A preventive maintenance action is initiated
when $\tnow + \tausnow$ would be earlier than the next planned evaluation time point.
We describe this dynamic and adaptive maintenance policy in more detail in Section~\ref{sec:operationalprocedure}.
%a flow chart for the policy is given in Figure~\ref{fig:procedure}.

The near*** optimal time to system re-evaluation $\tausnow$ is determined based on $\Rsysnow(t)$
by minimizing $\gnow(\tau)$, the expected cost rate for the current operational cycle.
%An operational cycle begins with system start-up,
%and ends when either preventive maintenance is carried out,
%or a failure of the system occurs, with subsequent corrective maintenance.
This criterion, as detailed in Section~\ref{sec:costrate},
%only assumes that $\Rsysnow(t)$ is given,
only assumes that a RLD is given,
and thus is not tied to our choice for the component models.
One could also consider alternative optimality criteria to determine $\tausnow$;
when safety is paramount one could, e.g., determine $\tausnow$ such that
the probability of system failure is at most at some very low pre-determined level.

Section~\ref{sec:optim} then focuses on our choice for the component models and the resulting form for $\Rsysnow(t)$,
and shows how $\tausnow$ is numerically determined in this situation.
%Numerical examples comparing results for three exemplary failure histories are given in Section~\ref{sec:examples},
%and a small simulation study is presented in Section~\ref{sec:sim}.

\begin{figure}
\centering
\begin{tikzpicture}
%[tausnow/.style={|-|, line width=0.5mm}]
[ tausnow/.style={line width=0.8mm},
  pfeil/.style={-latex', line width=0.5mm, shorten >=1mm}] 
\draw[-latex', very thick] (-0.2, -0.5) -- (5.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3, 4, 5}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (5,5);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw[tausnow] (2  , 2  ) -- (4.2, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw (2.4, -0.5) circle (0.8mm) edge[dotted] (2.4, 2.4);
%\node[draw,shape=diamond] (f1) at (2.4, -0.4) {}; % edge[dotted] (2.4, 2.4);
\draw[tausnow] (2.4, 2.4) -- (3.9, 2.4) node[at start, left] {$\tau_*^{(0.24)}$};
\draw[tausnow] (3  , 3  ) -- (4.4, 3  ) node[at start, left] {$\tau_*^{(0.3)}$};
\draw (3.6, -0.5) circle (0.8mm) edge[dotted] (3.6, 3.6);
\draw[tausnow] (3.6, 3.6) -- (4.3, 3.6) node[at start, left] {$\tau_*^{(0.36)}$};
\draw[tausnow] (4  , 4  ) -- (4.7, 4  ) node[at start, left] {$\tau_*^{(0.4)}$};
\node (box1) at (1,4) {\parbox{12ex}{\small preventive\\ replacement\\ at $\tnow = 0.4$\\ as $\tau_*^{(0.4)} < \delta$}};
\draw[pfeil] (box1) edge[out=20, in=120] (4,4);
\begin{scope}[xshift=7cm]
\draw[-latex', very thick] (-0.2, -0.5) -- (3.5, -0.5) node[below] {$t$};
\draw (0, -0.4) -- (0, -0.6) node[below] {$0$};
\foreach \x in {1, 2, 3}
 {\draw (\x, -0.4) -- (\x, -0.6) node[below] {$0.\x$};
  \draw[dotted] (\x, -0.4) -- (\x, \x); }
\draw[thick, decorate, decoration=brace] (1, -1) -- (0, -1) node[midway,below] {$\delta$};
\draw[dashed] (0, 0) -- (3,3);
\draw[tausnow] (0  , 0  ) -- (2.3, 0  ) node[at start, left] {$\tau_*^{(0)}$};
\draw[tausnow] (1  , 1  ) -- (2.9, 1  ) node[at start, left] {$\tau_*^{(0.1)}$};
\draw (1.4, -0.5) circle (0.8mm) edge[dotted] (1.4, 1.4);
\draw[tausnow] (1.4, 1.4) -- (2.8, 1.4) node[at start, left] {$\tau_*^{(0.14)}$};
\draw[tausnow] (2  , 2  ) -- (3.3, 2  ) node[at start, left] {$\tau_*^{(0.2)}$};
\draw[fill] (2.7, -0.5) circle (0.8mm) edge[dotted] (2.7, 2.7);
\node (box2) at (1,4) {\parbox{13ex}{\small corrective\\ replacement\\ at $\tnow = 0.27$\\ due to system failure}};
\draw[pfeil] (box2) edge[out=10, in=90] (2.7,2.7);
\end{scope}
\end{tikzpicture}
\caption{Two exemplary timelines for the suggested maintenance policy.
The horizontal bars depict $\tausnow$,
the time to the next economically optimal evaluation of the system RLD,
for subsequent times $\tnow$.
The times $\tnow$ for which $\tausnow$ is evaluated are
at regular intervals $m \delta, m \in \naturals_0$ (trigger 1),
and at the time of component failures (trigger 2),
which are marked by a circle on the time axis.
Failures that lead to the whole system failing (trigger 3) are marked by a filled circle.}
%The calculation of $\tausnow$ is described in detail in Section~***.}
%\begin{tikzpicture}\draw (0,0) circle (0.8mm);\end{tikzpicture}
\label{fig:timeline}
\end{figure}

\subsection{Two exemplary timelines}
\label{sec:policy-example}

Figure~\ref{fig:timeline} shows two examplary time lines,
starting each with a new system (operational cycle) at $t=0$.
The left timeline leads to preventive maintenance,
the timeline on the right to corrective maintenance.

As described in Section~\ref{intro},
the health of the system is re-evaluated at three types of triggers.
Triggers of type (1) are the evenly spaced planned evaluation time points $m\delta$, where $m \in \naturals_0$,
giving the time granularity at which maintenance actions can be reasonably initiated.***
%Let $\tthresh$ be a threshold time span chosen for practical reasons.
%used to decide when maintenance is initiated, i.e.,
%a time span chosen to reflect operational practicalities.
The times $m\delta$ are indicated by vertical tick lines on the time axis in Figure~\ref{fig:timeline},
where $\delta = 0.1$.
The moments of failure of a component form the other two types of triggers.
A component failure after which the system still functions is a trigger of type (2),
depicted as a (non-filled) circle on the time axis.
A filled circle indicates a trigger of type (3),
which is a component failure that causes the whole system to fail.

For each trigger of type (1) and (2),
the system health is evaluated by calculating $\tausnow$,
the currently optimal time to re-evaluation, %$\tausnow$ is %calculated,
visualized by the thick horizontal bars in Figure~\ref{fig:timeline}.
%The details of calculating $\tausnow$ are described in detail in Sections~\ref{sec:costrate} and \ref{sec:optim}.***
For a type (3) trigger, the system health evaluation just corresponds to acknowledging that the system has failed.
%/ to the diagnosis/insight*** of system failure.
%and calculation of $\tausnow$ is 
For triggers of type (1) and (2),
the calculated $\tausnow$ is compared to the time to the next planned evaluation time point.
When $\tausnow$ is shorter than this time,
preventive maintenance of the system is initiated.

In the timeline on the left of Figure~\ref{fig:timeline},
$\tausnow$ is re-evaluated at times $\tnow = 0.1, 0.2, 0.24, 0.3, 0.36, 0.4$,
where $0.24$ and $0.36$ correspond to component failure times.
Note that the failure at $\tnow = 0.24$ substantially shortens $\tausfun{0.24}$,
such that $0.24 + \tausfun{0.24} < 0.2 + \tausfun{0.2}$,
i.e., the optimal moment of re-evaluation has moved backwards in time.
This illustrates that new insights drawn from a component failure
(regarding the reliability block diagram as well as the component model)
may have considerable influence on the system RLD
and the $\tausnow$ that is derived from it.
The component failure at $\tnow = 0.36$ leads to a further shortened $\tausfun{0.36}$,
such that $\tausfun{0.36} < 0.1 = \delta$.
However, this does not lead to an immediate decision for preventive maintenance,
since $\tausfun{0.36}$ is compared to the time to the next planned evaluation at $t = 0.4$.
The decision for preventive maintenance is instead made at $\tnow = 0.4$,
as only then it is not economical any more to wait for the next planned evaluation at $t = 0.5$.

The timeline on the right of Figure~\ref{fig:timeline} illustrates an operational cycle ending with corrective maintenance.
Here, the component failure at $\tnow = 0.27$ leads to system failure.
The size of $\tausfun{0.2}$ indicates that the component failure that happens at $\tnow = 0.27$
had been deemed very unlikely at time $\tnow = 0.2$.
but then nevertheless occured at $t = 0.27$.

\subsection{Formal*** / Detailed description of the policy}
\label{sec:operationalprocedure}

***below two pars towards the end?

We assume that both preventive and corrective maintenance result in an (as good as) new system state by replacing all components,
such that the system begins a new operational cycle always under the same conditions.
At first sight, replacing a complete system when only some parts of it are defective may seem strange.
However, there are many real life examples, including from daily live.
So called complete clustering \citep{2017:oldekeizer}
may be optimal in case of a very strong economic dependence between the different parts of a system,
e.g., due to a very high fixed set-up cost independent of the maintenance activities to be done,
as is the case of installations/facilities*** used in the generation and distribution of oil and gas.
Note that often for safety reasons, the latter installations/facilities*** are monitored continuously.
There may be also technical dependencies between parts of a system that may require combined replacement:
replacing the cassette of a bike often also requires to replace the chain,
and the tires of an airplane are required to have the same thickness.
But also complete systems are replaced because replacing one or more of its parts may take much longer,
which may result in big production losses.
Another reason can be that there may be a high probability that when individual parts are replaced,
other parts will be damaged/have to be damaged***, requiring their replacement as well.

Replacement schemes that do not replace all components during maintenance
would require to account for the different ages of components in the system
at the start of a new cycle.
While this is in principle possible in our approach,
exploring such selective replacement schemes is out of scope for this paper.
Optimizing over replacement schemes is, in our view, a higly interesting topic that merits an investigation of its own.
We will return to this in the conclusion (Section~\ref{sec:outlook}).

@@

Figure~\ref{fig:procedure} depicts the flow chart for the policy,
indicating the decisions that are repeatedly encountered in a single operational cycle.
The flow chart also contains the loop back to the start of a new operational cycle.

%***Consider a set of evaluation time points $\tnow$.
Consider a grid of planned evaluation time points $\{m \delta : m \in \naturals_0\}$,
%where $m = 0, 1, 2, \ldots$,
%and $\delta$ sufficiently small to be negligible on the system lifetime scale.
with $\delta$ a sufficiently small time increment.
During an operational cycle,
$\tausnow$ is usually recalculated at times $\tnow = m \delta$, $m = 0, 1, 2, \ldots$.
%where the time increment $\delta$ should be small enough to be negligible on the scale of system lifetime.
However, if a component fails before the next $\tnow$ on the grid,
$\tnow$ is set instead to the exact failure time $t_{k,i}$.
Next, we check whether the system has failed due to this component failure.
If the system has failed, a corrective maintenance action is carried out, incurring cost $c_c$.
If the system has not failed, we calculate $\tausnow$ for the current off-grid time $\tnow = t_{k,i}$,
and move back onto the grid afterwards,
unless there is another component failure before the next planned evaluation time.

The calculation of $\tausnow$ for a fixed $\tnow$ resembles the calculation
of the maintenance interval in an age based policy by trading off the costs of preventive and corrective maintenance
(see Section~\ref{sec:costrate} below).
However, because $\tausnow$ is derived from the current $\Rsysnow(t)$,
our policy is adaptive and dynamic like a CBM policy. 
When computation of the RLD is fast,
frequent recalculation of $\tausnow$ is feasible,
%Then, by evaluating the unit cost rate function $\gnow(\tau)$ (see Section~\ref{sec:costrate} below) on a discrete grid,
%$\tausnow$ can be approximated with a simple grid search.
%because we use a fast discrete approximation of the unit cost rate function $\gnow(\tau)$,
%and determine $\tausnow$ with a simple grid search.
%Updating $\tausnow$ frequently is useful because,
and it is useful because,
even in absence of failures of system components,
all components age, and also non-failure adds information to the component models,
reducing uncertainty.
%Both aspects influence $\Rsysnow(t)$ and thus $\tausnow$,
%as is visible in the top panel of Figure~\ref{fig:tauhist1fig2T},
%which gives a numerical example described in more detail in Section~\ref{sec:examples}.
%An alternative would be to update $\tausnow$ only when a component fails,
%but as a (near) real-time update of $\tausnow$ is possible and useful,
%as non-failed components still can be used to update component models ($\nknow$ and $\yknow$) via right-censored observation $\tpnow$.
%
%As can happen for an age-based policy, the derived $\gnow(\tau)$ may also be monotonely decreasing.
%In this case, it is, at the moment $\tnow$, optimal to correctively maintain the system.
%This means that our approach is not only capable of finding the optimal moment for preventive maintenance,
%but also capable of indicating when corrective maintenance is the better option.
%i.e., capable of choosing the maintenance policy.

@@

In both cases, we decide to maintain the system preventively
when the optimal time to re-evaluation is closer to now than the next time we intend to re-evaluate $\tausnow$,
since otherwise, in waiting to the next planned evaluation time,
one would exceed the optimal system failure risk 
as determined by the trade-off made via $\gnow(\cdot)$.
When $\tausnow$ is instead further in the future than the next planned evaluation time,
we can safely continue to the next planned evaluation time,
without risking to miss the cost-optimal moment to preventively maintain the system.

At the end of each operational cycle, i.e.,
after maintaining the system either preventively or correctively,
the component information gained during the completed operational cycle is added to the component knowledge base
by updating the parameters $\nk$ and $\yk$ accordingly,
%using failure and censoring times as of the end of the cycle.
such that $\nkz$ and $\ykz$ for the next operational cycle
account for the (censored) lifetimes observed during the previous operational cycles.
%We assume that both planned and unplanned maintenance action takes negligible time,

%
%As we use a one-cycle criterion, the time both preventive and corrective maintenance actions require
%does not matter directly for the determination of $\tausnow$.
%Longer downtime and other negative effects of corrective maintenance
%are instead accounted for through the costs parameters $c_p$ and $c_c$ used in the trade-off leading to $\tausnow$,
%as described next.

@@

To determine the optimal time to maintenance $\tausnow$,
we use the expected one-cycle cost rate 
\citep{1984:ansell-bendell-humble,1996:mazzuchi-soyer,2006:coolen-schrijner-coolen}
as the unit cost rate.
Although a different, renewal theory based way to calculate the unit cost rate is often used
in CBM literature \citep[e.g.,][]{2013:si-et-al,2011:kim-et-al},
%As we discussed in the Introduction,
we use the one-cycle cost rate as it is the most appropriate for our situation,
where $\tausnow$ changes frequently.
